---
title: "&nbsp;"
output:
  html_document:
    toc_float: false
    css: style.css
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, error = FALSE )
## read in libraries
source("libraries.R")
## read in data
source("data.R")
```

## Introduction

During the 2015 IPCC COP21 meeting, countries from around the world agreed that globally GHG emissions are rising rapidly with resulting warming that needs to be limited to a 1.5° C increase over pre-Industrial levels. Asian economies were among those leading the call (Coca, 2015).  Asian leadership may be because of the high environmental impact rapid development has brought to the region.  Among all regions Asia’s energy use and emissions have risen the most rapidly over the past few decades.  From 1990 to 2013, Asia’s cumulative share of total contributions of carbon from fossil fuel, cement manufacture and gas flaring emissions (historically) rose from 9.2% to over 19%, exceeding those of Western Europe of 14.4%, but not yet reaching the contributions of North America of 30%. (Boden et al, 2016).  To meet the goal of the agreement, urgent action is needed.   

```{r}
br()
div(class="image-overlay",
img(src = "images/index_assets/solar_break.png")
)
br()
```

Economic growth and urbanization are highly correlated with energy use and GHG emissions levels (for review see, Seto et al, 2014).  Asian economies that have experienced this growth are responding to mitigation needs (Coca, 2015).  While studies suggest that there is significant potential for cities to reduce global emissions (Creutzig, et al 2015), effective policies to control GHG emissions, require an understanding of the factors that induce energy use and subsequent GHG emissions at the finest geographic resolution possible (Gurney, et al 2015).  

This project identifies the changes in energy use by source (residential, commercial, industrial and transportation) for sub-city scale areal units over time.  Socio-economic, political and institutional and biophysical factors (i.e., wealth/income, land use change, population, population density, fuel mix-carbon intensity, energy intensity, transit alternatives, policies, built environment, Heating and Cooling Degree Days, etc.,) help explain changes within each sub-city area and for the different case study city and metropolitan regions.   


#### Asian urban GHG emissions  

GHG emissions from the region are significant and the major metropolitan centers are
large and growing contributors. In most cases, national and urban emissions are
increasing, although the APN research teams identified stable emissions over the past
few years in Beijing and Tokyo.  

In the rapidly developing cities (Bangkok, BHT), important activities related to the
growth of emissions include: 1) the building of cities and subsequent creation of
concrete-related CO 2 emissions; 2) vehicle (passenger and freight) use; 3) industrial
manufacturing energy use and industrial processes and 4) low but growing residential
consumption. Within these urban centers there is significant difference among sub-city
units. It seems that industrial centers and new commercial centers have the highest
emissions levels. This is probably due to the economic activities and demand for
transportation in these areas. That is, industry and transportation are important sectors
of GHG emissions in Asian cities. At the same time, the need for air conditioning should
not be overlooked. The comfort of the population is a critical factor and given that
residential energy use is low, increasing cooling should be prioritized to increase the
quality of urban life, particularly for lower income groups.  
```{r}
br()
div(class="image-overlay",
img(src = "images/index_assets/solar_break.png")
)
br()
```
In the more developed Asian cities (Taipei, Seoul and Tokyo), emissions are related to
buildings, transportation and residential energy use. Emissions from these cities are
lower per capita than those of some rapidly developing cities. For example, Tokyo’s per
capita emissions are lower than those of Beijing. Kuala Lumpur’s emissions per capita
are higher than those of New York City.  

Given the differences in CO 2 emission sources, there are different policy options for
different types of cities. For example, in more developed cities where emission levels
are decreasing, given this high embedded energy and CO 2 in buildings reuse could be
an important way to lower emissions and preserve historical infrastructure. This is 
particularly important given the energy and emissions concentrated in new concrete and
steel structures. In cities of rapid growth and industrial development, policies to
regulate industries (such as those in the BHT region) are more important than building
retrofits.

#### Potential policy pathways  

The major Asian metropolitan centers are leading national low-carbon efforts. The
studies in this project identified Tokyo and Seoul as national leaders in carbon reduction
strategies. Taipei and Bangkok are also implementing policies. This suggests that
some of the major metropolitan cities are leading the region’s efforts in meeting the
Paris Agreement. Specific policies for low-carbon development across these centers
varies and should do so. Certainly, all cities share the need to reduce emissions from
growing passenger car use. While many Asian cities are already dense and compact,
the temptation of following the sprawled suburban development model and passenger
car pathway is strong. This may be beyond the control of local governments. Japan,
for instance, was able to reduce its transportation burden due to national policies that
limited car ownership early on during development. Moreover, Japan’s “top runner”
program has been successful in encouraging efficiencies in new automobiles. Asian
governments could learn from the Japanese model. Tokyo is a livable city with access
to all areas through transit.  

Industrial development, particularly in cities that are industrial centers, is an important
contributor to economic wealth, but emissions from industrial processes can be
regulated to help reduce emissions. In this case, both urban planning and city
regulations requiring lower emissions is possible. Enhancing laws that encourage
energy efficiency in both energy use and industrial processes could help here. Finding
ways to lower carbon related consumption is challenging. Some options include
enhancing the sharing economy, which has enhanced potential in dense settlements
compared to more dispersed spatially organized units and encouraging the circular
economy. In parts of Asia the rates of recycling and waste reduction are already high,
demonstrating the applicability of this model.  

#### Future research suggestions  

The review and papers in the project demonstrate the importance of sub-city and
sectorial GHG analyses. The future of urban GHG emissions analysis is certainly a
focus on higher resolution spatially disaggregated analyses. Promising studies using
satellite images that can pick up CO 2 emission signals are interesting and potentially
extremely useful. There will still be the need, however, for consumption related
emissions analytics. Nevertheless, identifying neighborhoods and areas of high 
emissions levels allows urban stakeholders to target these areas for reductions and
efficiency exercises.  

While the larger cities make up the lion’s share of emissions across the region and the
world, they are also typically the most efficient and lower per capita GHG emission
urban centers. Interest should also be targeted to medium size and smaller cities.
Policies from the larger cities serve as models for other cities and more emphasis could
be focused on policy migration from larger to smaller centers. This will probably require
a transfer of skills and capacities.  

```{r}
br()
div(class="image-overlay",
img(src = "images/index_assets/solar_break.png")
)
br()
```  

Finally, this research identified the need for more policy-oriented research to identify
potential pathways most relevant for different types of Asian cities. There are no one-
size-fits-all policies and each city will need to develop low carbon trajectories based
upon its particular history and sources of emissions. Therefore, more work is needed to
analyze the effectiveness of various policies and the ability of these policies to be
transferred to cities of similar type.  

Asia will remain the center of industrial activity, population growth and increasing CO 2
emissions over the next few decades. It is therefore urgent to identify ways in which the
region’s cities can become more efficient and less polluting. There are both hopeful and
threatening trends emerging. Whether the region can leap-frog over the problems
experienced by the developed world remains uncertain. Work on urban GHG emissions
will continue to play an important role into the medium-term future.

